\section{Notation}

For the rest of this course, $\N$ contains 0.

\section{Introduction}

\begin{definition}
  Unless stated otherwise, $G \ss \C$ and $H \ss \R^n$ are arbitrary domains.
\end{definition}

\begin{definition}
  A function $f \col G \to \C$ is \emph{analytic}, if for any $z_0 \in G$ there exists $r > 0$ such that $D_r(z_0) \ss G$, and
  $$ f(z) = \sum_{n \in \N_0} a_n (z - z_0)^n $$
  for some $\b{a_n}$ and every $z \in \D_r(z_0)$. 
\end{definition}

\begin{definition}
  $\phi \col G \to \C$ is \emph{holomorphic} at $z_0$, iff exists
  $$ \phi'(z_0) = \lim_{h \to 0} \frac{\phi(z_0+h)-\phi(z_0)}{h}. $$
  Here $h \in \C$.
  If a function $f$ is holomorphic at every point of $E \ss \C$, we write $f \in \Hol E$.
\end{definition}

\begin{definition}
  A function $f \in \Hol \C$ is called \emph{entire}.
\end{definition}

\begin{theorem}[Cauchy-Riemann equations]
  $f \col G \to \C$ is holomorphic at $z_0$ iff
  \begin{align*}
    \frac{\pd u}{\pd x} &= -\frac{\pd v}{\pd y}, x  x x&
    \frac{\pd u}{\pd y} &= \frac{\pd v}{\pd x}
  \end{align*}
  at $\p{x_0, y_0}$,
  where $u(x, y)+iv(x,y) = f(x+iy)$ and $z_0 = x_0+iy_0$.
\end{theorem}
That is, the Jacobi matrix of $u \times v$ is in the image of the standard embedding of $\C$ into $\on{M}_2(\R)$:
$$ a+ib \mapsto \begin{pmatrix}
  a & b \\
  b & -a
\end{pmatrix}
$$

\begin{proof}[Has been proven in semester II.]
\end{proof}

\begin{lemma}
  If $f \col G \to \C$ is analytic, then it is holomorphic.
\end{lemma}

\begin{proof}
  The series for $f(z)$ can be differentiated.
\end{proof}

\begin{theorem}[Cauchy]
  Let $f \col G \to \C$ be holomorphic.
  Then it is analytic at every $x_0 \in G$, with the radius of convergence $r$ being equal to $r = \dist\p{x_0, \C \sm G}$. 
\end{theorem}

The proof will be given shortly.

\section{Differential forms}

\subsection{A reminder}

\begin{definition}
  If we have a form
  $$ \go(h) = \sum_I \go_I \cdot h^I, $$
  its integral (also a form) is defined as
  $$ \int \go = \int \sum_I \go_I \circ x \cdot D_I, $$
  where $D_I$ is the determinant of the rows $I$ of the Jacobi matrix $\d x$.
\end{definition}

\subsection{Integral of a form along a path}

\begin{definition}[integral along a curve] 
  Let $\gg \col [a, b] \to \R^n$ be a $C^1$ function. If $\phi = f_1 \d x_1 + \dots + f_n \d x_n$, where $f_i$ are continuous complex functions on $G$, then
$$ \int_\gg \phi := \sum_{j=1}^n\ \int_{t=a}^b f_j\p{\gg(t)} \gg'_j(t). $$
\end{definition}

Evidently, the integral over a one-dimensional submanifold does not depend on parametrisation. We will further use that to write integrals over subsets of $\C$, not curves.

\begin{remark}
  We may only require that $\gg$ is rectifiable.
  In this case, the integral will be in the sense of Stieltjes:
  $$ \int_\gg \Phi = \sum_{j=1}^n \int_{t=a}^b f_j\p{\gg(t)} \dd \gg_j. $$
  We will not need this during this course.
\end{remark}

\begin{lemma}
  Integral of differential forms along a path is linear with respect to the form.
\end{lemma}

\begin{proof}
  Evident.
\end{proof}

\begin{lemma}[change of variables]
  Let $\ga \col [c, d] \to [a, b]$ be a $C^1$-homeomorphism, and $\wt \gg = \gg \circ \ga$. Then
  $$ \int_{\wt \gg} \phi = \pm \sum_{j=1}^n \ \int_{t=c}^d f_j \circ \gg \circ \ga(s) \cdot \gg'_j\circ\ga(s) \cdot \ga'(s). $$
  The sign here depends on whether $\ga$ is increasing or decreasing.
\end{lemma}

\begin{proof}
  Follows from the change-of-variables formula for the Riemann integral.
\end{proof}

\begin{definition}
  Let $\ga, \gb$ be $C^1$-paths. Their \emph{concatenation} $\ga \gb$ is defined as
  $$ \gg(t) =
  \begin{cases}
    \ga(t), & t \in [a, b], \\
    \gb \circ \phi(t), & t \in [b, c],
  \end{cases}
  $$
  where $\phi \col [b, c] \to [a', b']$ is a homeomorphism.
\end{definition}

\begin{definition}
  A path $\gg$ is \emph{piecewise smooth}, iff it is a finite concatenation of smooth paths.
\end{definition}

\begin{definition}
  The integral of a form along a piecewise smooth path is the sum of integrals over its components.
\end{definition}

\begin{definition}
  If $\phi = \sum \phi_j \d x_j$ is a differential form, we denote
  $$ \n{\phi} = \sqrt{\sum_{j=1}^n \phi_j^2}. $$
\end{definition}

Differential 1-forms are simply functions between Euclidean spaces.

\begin{theorem}[principal estimate]
  If $\gg$ is piecewise smooth and $\phi$ is a continuous differential 1-form in a neighbourhood of $\im \gg$, then
  $$ \a{\ \int_\gg \phi\ } \le l(\gg) \cdot \sup_{x \in \im \gg} \n{\phi(x)}. $$
\end{theorem}

\begin{idea}
  CBS.
\end{idea}

\section{Antiderivatives}

\begin{definition}
  Let $\go$ be be a differential 1-form in $G$.
  Its \emph{derivative} is the form
  $$ \d \go = \sum_{j=1}^n \frac{\pd \go_j}{\pd x} \d x_j. $$
\end{definition}

\begin{definition}
  Let $G \ss \R^n$ be a differential form.
  $F \col G \to \C$ is called the \emph{antiderivative} of $\Phi$, iff $\d F = \Phi$. 
\end{definition}

\begin{definition}
  A differential form $\go$ is
  \begin{enumerate}
    \item \emph{exact}, iff it has an antiderivative;
    \item \emph{closed}, iff every point $x \in G$ has a neighbourhood where $\go$ is exact.
  \end{enumerate}
\end{definition}

  Observe that this definition differs from the one given in the semester III. This one is more general: the previous one depended on smoothness.

\begin{lemma}
  Suppose $\go$ is a $C^1$ differential 1-form in $G$.
  Then $\go$ is closed iff
  $$ \pd_i \go_j = \pd_j \go_i $$
  for all $i, j \in \b{1, \dots, n}$.
\end{lemma}

\begin{proof}[Proof of $\Rightarrow$.]
  Locally, we have an antiderivative $\Omega$, so $\pd_j \Omega = \go_j$.
  Then
  $$ \pd_i \go_j = \pd_{i} \pd_j \Omega = \pd_j \pd_i \Omega = \pd_j \go_i. $$
\end{proof}

\begin{proof}[Proof of $\Leftarrow$.]
  We know from semester III that every differential form $\go$ such that $\d \go = 0$ is exact. But this is true of $\go$.
\end{proof}

\begin{lemma}
  Let $\gg$ be a piecewise smooth path with $\im \gg \ss G$ and ends $A, B$. Then
  \begin{equation}
    \label{NL}
    \int_\gg \d F = F(B) - F(A).
  \end{equation}
\end{lemma}

\begin{proof}
  From the Newton-Leibniz formula.
\end{proof}

\begin{theorem}
  Every two points in $G$ can be connected by piecewise linear path.  
\end{theorem}

\begin{proof}[A well-known fact.]
\end{proof}

\begin{definition}
  Let $\Phi$ be a differential form in a region $H \ss \R^n$.
  We call $H$ a \emph{$\Phi$-balanced}\footnote{My own term.} region, iff
  $ \int_\gg \Phi = 0 $
  for every closed curve $\gg$ with $\im \gg \ss H$.
\end{definition}

\begin{theorem}[reformulations of `exact']
  Let $\Phi$ be a differential form in $H \ss \R^n$ with continuous coefficients. Equivalent are:
  \begin{enumerate}
    \item $\int_\gg \Phi$ depends on $A$ and $B$ only.
    \item $H$ is $\Phi$-balanced.
    \item $\Phi$ is exact. 
  \end{enumerate} 
\end{theorem}

\begin{proof}[Proof of $3 \Rightarrow 2$.]
  See \eqref{NL}.
\end{proof}

\begin{proof}[Proof of $2 \Rightarrow 1$.]
  Concatenate paths between two points and get a closed path. But the integral (which is zero by hypothesis) splits into two. Next we use that it depends on the direction of the path.
\end{proof}

\begin{proof}[Proof of $1 \Rightarrow 3$.]
  Fix $A_0 \in G$. For any $x \in H$, let $\gg$ be a piecewise linear path $A_0 \leadsto x$. Define
  $$ F(x) = \int_\gg \Phi. $$
  Since the integral depends only on $x$, this is correctly defined function
  We assert that $F$ is an antiderivative for $\Phi$; that is, the partial derivatives of $F$ are components of $\Phi$.
  To see this, consider the path
  $$ A_0 \leadsto_\gg x \leadsto_\gb x+te_j, $$
  where the last part $\gb$ is linear.
  Then
  \begin{align*}
    \frac{F(x+te_j) - F(x)}{t}
    &= \frac{\int_\gg \Phi + \int_{\gb} \Phi - \int_\gg \Phi}{t}  \\
    &= \frac{1}{t} \int_{\gb} \Phi \\
    &= \frac{1}{t} { \sum_{k=1}^n\ \int_{\gt=0}^t f_k\p{x+\gt e_j} \gb_k'(\gt) } \\
    &= \frac{1}{t} \int_{\gt=0}^t f_j\p{x+\gt e_j} \\
    &\xrightarrow[t \to 0]{} {f_j(x)}.
  \end{align*}
\end{proof}

\begin{definition}
  We call a region $H \ss \R^2$ \emph{rectangle-astroid}\footnote{My own term.}, iff there exists $x_0 \in H$ such that for every $x \in H$ the 2-dimensional rectangle with sides parallel to the axes, having $x_0$ and $x$ as diametral points, lies in $H$ together with its closure. The rectangle in this context is called \emph{central}.
\end{definition}

This definition is long, but it highlights what we need to use to prove the following proposition for circles.

\begin{lemma}[addition to the theorem]
  Let $H \ss \R^2$ be a rectangle-astroid region. Then $H$ being $\Phi$-balanced is also equivalent to
  $$ \int_Q \Phi = 0 $$
  for every 1-dimensional central rectangle $Q$. 
\end{lemma}

\begin{idea}
  The integral over this rectangle is equal to zero, since it is closed. Conversely, we can find an antiderivative like in the proof of the theorem.
\end{idea}

\begin{theorem}[Cauchy, Morera]
  Let $\gg$ be a closed continuous curve with $\im \gg \ss G$.
  Then a function $f \col G \to \C$ is holomorphic iff
  $$ \int_\gg f = 0. $$
\end{theorem}

\section{Connectivity}

\begin{lemma}
  Every two points of a domain $H \ss \R^n$ can be connected by a piecewise-linear path.  
\end{lemma}

\begin{proof}
  Fix $x_0 \in H$ and put $A$ to be the set of all points reachable from $x_0$ by a piecewise-linear path over $H$. $A$ is open, since $H$ is: every point in $A$ is the centre of a ball in $H$, and balls are convex. The complement $H \sm A$ is open for the same reasons: take any point $x$ from there, there is a ball $B \ss H$ around it; if there was a point of $A$ in this $B$, we could connect it to $x$. Therefore, $A$ is open and closed; but it is not empty either, so $A = H$ by connectedness of the domain $H$.
\end{proof}

Recall the theorem on equivalence of linear connectivity and connectedness for locally linearly connected spaces. The proof is almost the same.

\begin{theorem}
  Every two points of a domain $H \ss \R^n$ can be connected by a $C^\infty$ path.   
\end{theorem}

We need to recall some stuff about convolutions for the proof.

\begin{definition}
  A family $\b{\phi_s}_{s > 0}$ of infinitely smooth functions $\R^n \to \R$ with compact support and such that
  \begin{align*}
    \int \phi_s &= 1, &
    \phi_s(x) &= \frac{\phi_1\p{x/s}}{s^n}
  \end{align*}
  for all $s > 0$ and $x \in \R^n$ is called a
  \emph{standard approximative unit} or a \emph{mollifier}.
\end{definition}

\begin{theorem}
  ~\begin{enumerate}
    \item A family $\b{\phi_\square}$ exists.
    \item Let $f \col \R^n \to \R$ be a continuous function.
  Then the functions $\phi_s * f$ converge to $f$ uniformly with $s \to 0$ and are infinitely smooth.
  \end{enumerate}
\end{theorem}

The \emph{proof} was given in the third semester.
Now we start with the main theorem.

\begin{proof}
  Let $\gg \col [a, b] \to H$ be a continuous path $A \leadsto B$. Continue $\gg$ to a continuous path $\R \to H$ by setting
  $$
  \gg(t) =
  \begin{cases}
    \gg(a), & t < a, \\
    \gg(b), & t > b, \\
    \gg(t), & t \in [a, b].
  \end{cases}
  $$
  Let $\phi_\square$ be a standard approximative unit for functions on $\R$, and put for all $s > 0$
  $$ \wh \gg_s(x) = \p{\phi_s*\gg}(x), $$
  where $*$ denotes component-wise convolution.
  Fix $\eps > 0$, $a_2 < a$, and $b_2 > b$.
  By the theorem on approximating with units, if $s$ is small enough, we have $\a{\wh \gg_s(t) - \gg(t)} < \eps$  for all $t \in [a_2, b_2]$.
  This $\eps$ can be chosen in such a way that the path $\wh \gg_s$ does not leave the domain $H$.
  Further, choose $a_2, b_2$ such that
  \begin{align*}
    \wh \gg_s\p{a_2} &= \gg(a), &
    \wh \gg_s\p{b_2} &= \gg(b).
  \end{align*}
  \wtf
  This ensures  $\wh \gg|_{\q{a_2, b_2}}$ is indeed the path we need.
\end{proof}

\section{Closed forms and balanced regions}

\begin{theorem}[reformulations of `closed']
  Let $\Phi$ be a differential form in $H \ss \R^n$ with continuous coefficients $f_j$. The following are equivalent:
  \begin{enumerate}
    \item $\Phi$ is closed.
    \item Every $x \in H$ has a $\Phi$-balanced neighbourhood $U \ss H$.
  \end{enumerate}
  In case $n = 2$, two more reformulations are true:
  \begin{enumerate}
    \setcounter{enumi}{2}
    \item For every $x \in H$, there exists a rectangle-astroid region $B \ni x$ such that $\int_Q \Phi = 0$ for any central rectangle $Q$.
    \item $\int_Q \Phi = 0$ for any rectangle $Q$ such that $\Cl Q \ss H$. 
  \end{enumerate}
\end{theorem}

\begin{proof}[Proof of $3 \Rightarrow 4$.]
  Split the rectangle $Q$ into equal four, $\b{Q_i}$.
  Then the integral over $Q$ is equal to the sum of integrals over $\b{Q_i}$.
  Cover the compact $\Cl Q$ with `good' rectangle-astroid regions which lie in $H$ completely (they exist by hypothesis).
  Let $\gd > 0$ be the Lebesgue number of this cover.
  Continue to split the rectangles into four until each of them is less than $\gd$ in diameter.
  Now it is clear that the integral over $Q$ is zero itself.
\end{proof}

\begin{proof}[Proof of $4 \Rightarrow 3$]
  $G$ is open.
\end{proof}

\section{Change of basis}

Let $z = x+iy$. Then
\begin{align*}
  \d z &= \d x + i \d y &
  \d \ol z &= \d x + i \d y,
\end{align*}
so
\begin{align*}
  \d x &= \frac{\d z + \d \ol z}{2}, &
  \d y &= \frac{\d z - \d \ol z}{2}.
\end{align*}
Now let $\phi = u \d{x} +v\d{y}$ be a 1-form, defined in $H \ss \R^2$. Then, if $\phi = \d{\Phi}$ for a function $\Phi \col H \to \C$, we have
\begin{align*}
  \Phi &= \frac{\pd_1 \Phi - \pd_2 \Phi}{2} \d z
  + \frac{\pd_1 \Phi - \pd_2 \Phi}{2} \d \ol z
\end{align*}
by direct computation.
By analogy, we define
\begin{definition}
  \begin{align*}
  \pd_z \Phi &:= \frac{\pd_1 \Phi - i \pd_2 \Phi}{2} &
  \pd_{\ol z} \Phi &:= \frac{\pd_1 \Phi + i \pd_2 \Phi}{2}.
\end{align*}
\end{definition}
Let $\Phi = p + iq$.
It then can be derived that
\begin{align*}
  \pd_{\ol z} \Phi
  &= \frac{\pd_1 p - \pd_2 q}{2}
  + i \frac{\pd_1 q + \pd_2 p}{2}.
\end{align*}
Therefore,
\begin{align*}
  \pd_{\ol z} \Phi = 0 
  \iff
  \begin{cases}
    \pd_1 p = \pd_2 q, \\
    \pd_1 q = -\pd_2 p.
  \end{cases}
\end{align*}
These are the Cauchy-Riemann equations.
Therefore,
\begin{lemma}
  A function $\Phi \col G \to \C$ is holomorphic iff $\d{\Phi} = \pd_{z} \Phi \d{z}$.
\end{lemma}

We can also prove the following:
\begin{lemma}
  Let $\ga \d z$ be a form in $G$.
  It is exact iff there exists a holomorphic function $A \col G \to \C$ such that $A' = \ga$.
\end{lemma}

\begin{proof}[Proof of $\Rightarrow$.]
  Let $A$ be the antiderivative.
  $\ga \d{z} = \ga\d{x}+i\ga\d{y}$.
  Then $\pd_1 A = \ga$, $\pd_2 A = i\ga$,
  so
  \begin{align*}
    A' = \pd_z A &= \frac{\pd_1 A - i\pd_2 A}{2} = \ga, &
    \pd_{\ol z} A &= \frac{\pd_1 A + i\pd_2 A}{2} = 0.
  \end{align*}
\end{proof}

\begin{lemma}[a variation of the principal estimate]
  Let $\ga \col G \to \C$ be a function, $\gg \col [a, b] \to G$ a $C^1$ path.
  Then
  $$ \a{\int_\gg \ga \d{z}} \le l(\gg) \cdot \sup_{z \in \im \gg} \a{\ga(z)}. $$
\end{lemma}

\begin{idea}
  Use the principal estimate and the identity $\gg' = \gg'_1 + i \gg'_2$.
\end{idea}

\section{Cauchy's theorem on closedness}

\begin{theorem}[Cauchy, on closedness]
  If $f \col G \to \C$ is holomorphic, then the form $f \d{z}$ is closed.
\end{theorem}

That is, locally, it has antiderivatives. The proof spans the several following pages and requires a few lemmas.

\subsection{The case of continuous derivative}

\begin{lemma}
  Suppose $f'$ is continuous. Then the form $f \d{z}$ is closed.
\end{lemma}

{While this might seem to give a hint of our further course of action, we won't be so blunt as to prove the continuity of $f'$ directly.}

\begin{idea}
  Indeed, as we know, the closedness is then equivalent to the equality
  $$ \frac{\pd f}{\pd y} = i\frac{\pd f}{\pd x}. $$
  This is straightforward to show using Cauchy-Riemann equations.
\end{idea}

\begin{example}
  \label{closed and not exact}
  The form ${\d z}/{z}$ is closed and not exact.
  $f' = -1/z^2$ in this case is a continuous function. By the previous lemma, $f$ is closed (in fact, its antiderivatives are logarithms). Now consider the unit circle $\S^1$. By parametrising with $e^{i\square}$, we can easily check that 
  $$ \int_{\S^1} \frac{\d z}{z} = 2 \pi i. $$
  But this means we have found a non-balanced region of $\C$, so $\d z / z$ is not exact.
\end{example}

\subsection{Indices}

\begin{lemma}
  Let $C = z_0 + r\S^1$ for some $r > 0$. Then
  \begin{align}
      \int_C \frac{\d z}{z - z_1} =
      \begin{cases}
        0, & \a{z_1-z_0} > r, \\
        2 \pi i, & \a{z_1-z_0} < r.
      \end{cases}
  \end{align}
\end{lemma}

\begin{proof}
  Consider the case $\a{z_1-z_0}>r$. Luckily, the form $\frac{\d z}{z - z_1}$ is closed in $H = \C \sm \b{z_1}$. This $H$ contains a rectangle around the square $C$. Every closed form is exact within this rectangle by a theorem from semester 3.
  
  Suppose, for now, $\a{z_1-z_0}<r$.
  We reduce this to the case $z_0 = z_1$, which has been considered in the example on page \pageref{closed and not exact}.
  Then
  \begin{align*}
    \int_C \frac{\d z}{z - z_1}
    &= \int_C \frac{\d z}{\p{z-z_0}-\p{z_1-z_0}} \\
    &= \int_C \frac{\d z}{z - z_0} \cdot \frac{1}{1 - \frac{z_1-z_0}{z-z_0}} \\
    &= \int_C \frac{\d z}{z-z_0} \cdot \sum_{k\in \N} \p{\frac{z_1-z_0}{z-z_0}}^k \\
    &= 2 \pi i + \sum_{k\in \N \sm 0} \int_C \frac{\d z}{z-z_0} \p{\frac{z_1-z_0}{z-z_0}}^k \\
    &= 2 \pi i.
  \end{align*}
\end{proof}

\subsection{The conclusion}

\begin{theorem}[Cauchy, on closedness]
  \label{Cauchy, on closedness}
  If $f \col G \to \C$ is holomorphic, then the form $f \d{z}$ is closed.
\end{theorem}

\begin{proof}
  Suppose otherwise: there exists a 2-dimensional rectangle $P \ss G$ with $I := \int_{\pd P} f \ne 0.$
  Subdivide it into four $\b{Q_i}$ such that
  $$ I = \sum_i \int_{\pd Q_i} f. $$
  For one of them, $Q_j$, the modulus of the integral is at least one fourth the $\a{I}$. Denote $P_1 = Q_j$. Continuing this sequence, we get diminishing $\b{P_j}$ with a single point $z_0$ in their intersection. The function $f$ is holomorphic at $z_0$, so we may write
  $$ f(z) = f(z_0)+f'(z_0)(z-z_0)+\phi(z), $$
  where $\phi(z) = o\p{z-z_0}$ with $z \to z_0$.
  Select $k$ such that $\a{\phi(z)} < \eps \a{z-z_0}$ for all $z \in P_k$.
  Then we have
  \begin{align*}
    \a{\frac{I}{4^k}}
    &\le\a{\ \int_{\pd P_k} f} \\
    &= \a{\ \int_{z \in \pd P_k} \p*[\big]{\ub{f(z_0)+f'(z_0)(z-z_0)}_{\text{these guys are exact in $P_k$}}\mathrel{+}\phi(z)}} \\
    &= \a{\ \int_{z \in \pd P_k} \phi(z)} \\
    &\le \eps \cdot \p{\Diam P_k} \cdot {S_1\p{\pd P_k}} \\
    &= \eps \cdot \frac{\p{\Diam P} \cdot S_1\p{\pd P}}{4^k}.
  \end{align*}
  But we thought that $I \ne 0$.
\end{proof}

\section{On correctible singularities}

\begin{lemma}[on correctible singularities]
  \label{correctible singularities}
  Let $a \in G$.
  Suppose the form $\go = f \d x + g \d y$ is closed in $G \sm \b{a}$, and the coefficients $f$ and $g$ are continuous in $G$. Then $\go$ is closed in $G$.
\end{lemma}

\begin{idea}
  Approximate integrals with smaller rectangles.
\end{idea}

\section{The minor integral formula of Cauchy}

\begin{theorem}[Cauchy, minor integral formula]
  \label{Cauchy, minor integral formula}
  Let $f \col G \to \C$ be holomorphic,
  $z_0, z_1 \in G$,
  $C = z_0 + r\S^1$,
  $\a{z_1 - z_0} < r$.
  Then
  $$ f(z_1) = \frac{1}{2 \pi i} \int_C \frac{f(z)}{z-z_1} \dd z. $$
\end{theorem}

`Probably the most important formula in complex analysis.' --- S.K.

The `greater' integral formula gives the same result for $C$ not necessarily a circle.

\begin{proof}
  Fix $z_0 \in G$.
  Consider
  $$
  h(z)
  =
  \begin{cases}
    \frac{f(z)-f(z_1)}{z-z_1}, & z \ne z_1 \\
    f'(z_1), & z = z_1.
  \end{cases}
  $$
  $h$ is continuous in $G$ and holomorphic in $G \sm \b{z_0}$.
  By Cauchy's theorem on closedness (page \pageref{Cauchy, on closedness}), the form $h \d z$ is closed in $G \sm \b{z_1}$.
  By the lemma on correctible singularities (page \pageref{correctible singularities}), it is also closed in all of $G$. Let $\wh C$ be a ball of slightly greater radius $r + \gd$, but still lying in $G$. Every closed form in $\wh C$ is exact, so
  $$ \int_C h \d z= 0. $$
  Rewriting this yields
  \begin{align*}
    f(z_1) \ub{\int_C \frac{\d z}{z-z_1}}_{=2\pi} = \int_C \frac{f(z)}{z - z_1} \d z.
  \end{align*}
\end{proof}

\section{Cauchy's theorem on analyticity}

\begin{theorem}[Cauchy, on analyticity]
  Let $f$ be holomorphic in $G$, $z_0 \in G$, $R = \dist\p{z_0, \pd G}$. 
  For all $k \in \N$, define
  $$ c_k = \frac{1}{2\pi i} \int_C \frac{f(z)}{\p{z-z_0}^{k+1}} \d z. $$
  Then
  $$ f(z) = \sum_{k \in \N} c_k \p{z-z_0}^k $$
  for all $z$ such that $\a{z-z_0} < R$.
  In particular, $f$ is analytic in $G$.
\end{theorem}

\begin{proof}
  Let $C$ be a circle around $z_0$ of radius $r < R$.
  By Cauchy's minor integral formula from page \pageref{Cauchy, minor integral formula}, for any $z$ inside of $C$ we have
  \begin{align*}
    f(z_1)
    &= \frac{1}{2\pi i} \int_C \frac{f(z)}{z-z_1} \d z \\
    &= \frac{1}{2\pi i} \int_C \frac{f(z)}{\p{z-z_0}-\p{z_1-z_0}} \d z \\
    &= \frac{1}{2\pi i} \int_C \frac{1}{z-z_0} \cdot \frac{f(z)}{1-\frac{z_1-z_0}{z-z_0}} \d z \\
    &= \sum_{k\in \N} \frac{1}{2\pi i} \int_C \frac{f(z)}{z-z_0} \cdot \p{\frac{z_1-z_0}{z-z_0}}^k \d z \\
    &= \sum_{k\in \N} \p{z_1-z_0}^k \cdot \p{ \frac{1}{2\pi i} \int_C \frac{f(z)}{\p{z-z_0}^{k+1}} \d z },
  \end{align*}
  which is desired.
  Transposing the sum with the integral is legit, since the series for geometric progression converges uniformly for all $z$.
\end{proof}

\begin{remark}
  In the analyticity theorem,
  $$ c_k = \frac{f^{(k)}(z_0)}{k!}. $$
  In particular,
  $$ f'(z) = \frac{1}{2\pi i} \int_{\pd B} \frac{f(\gz)}{\p{\gz-z}^2} \d \gz. $$
\end{remark}

\subsection{Morera's theorem}

\begin{corollary}[Morera's theorem]
  Let $f \col G \to \C$ be a continuous function.
  The following conditions are equivalent:
  \begin{enumerate}
    \item $f$ is analytic.
    \item $f$ is holomorphic.
    \item $f \d z$ is closed. 
  \end{enumerate}
\end{corollary}

%This, in particular, gives an alternative proof of the analyticity theorem.

\begin{proof}
  $1 \Rightarrow 2$ follows by differentiating the series, $2 \Rightarrow 3$ is the Cauchy's theorem on closedness from page \pageref{Cauchy, on closedness}. We now give a proof of $3 \Rightarrow 1$. By definition, the form $f \d z$ locally has an antiderivative $\Phi$. Then $\Phi$ is holomorphic, and $\Phi' = f$. By the analyticity theorem, $\Phi$ is holomorphic, which implies that $f$ is, too (simply differentiate the series). 
\end{proof}

\section{The mean value theorem}

\begin{lemma}[mean value theorem]
  If $f \in \Hol G$ and $z \in G$, then
  $$ f(z) = \frac{1}{2 \pi} \int_{t=0}^{2\pi} f\p{z+re^{it}} $$
  for all $0 < r < \dist\p{z, \pd G}$.
\end{lemma}

\begin{idea}
  Follows from the Cauchy's minor integral formula (page \pageref{Cauchy, minor integral formula}).
\end{idea}

\section{Maximum modulus principle}

\begin{theorem}[maximum modulus principle]
  Let $f \col G \to \C$ be holomorphic. Then $\a{f}$ has no strict maximum in $G$.
\end{theorem}

\begin{proof}
  Suppose $f$ has a non-strict maximum in $G$. Then
  \begin{align*}
    \a{f(a)}
    &= \frac{1}{2\pi} \a{\int_C f(z) \d z} \\
    &\le \frac{1}{2\pi} {\int_C \a{f(z)} \d z} \\
    &\le \a{f(a)}.
  \end{align*}
  Here every inequality must be an equality.
  Then $\a{f(z)} = \a{f(a)}$ for all $z$ in some disk $D$ around $a$.
  
  Suppose $f'(a) \ne 0$.
  Then $f$ is a local homeomorphism around $a$, which means it must map a ball in $\C$ into a ball in $\C$. But in any ball there are points with varying modulus.
  
  Therefore, $f$ is constant, what completes the proof.
\end{proof}

\section{Liouville's theorem}

\begin{theorem}[Liouville]
  A bounded entire function is constant.  
\end{theorem}

A powerful theorem.

\begin{proof}
  From principal estimate and the formula for $f'$:
  \begin{align*}
    \a{f'(z)}
    &\le \frac{M}{2\pi} \int_C \frac{r}{\p{r - \a{z}}} \d t \\
    &= \frac{Mr}{\p{r-\a{z}}^2} \\
    &\xleftarrow[r \to \infty]{} 0.
  \end{align*}
\end{proof}

\subsection{Principal theorem of algebra}

\begin{corollary}[principal theorem of algebra]
  $\C$ is algebraically closed.
\end{corollary}

\begin{proof}
  Suppose $p \col \C \to \C$ of $\deg p > 0$ has no roots: $\a{p} > \gd$ for some $\gd > 0$. Then $1/p$ is an entire function, and, as such, is either unbounded or constant. It is not constant, so it must be unbounded; but $1/\a{p} < 1/\gd$ --- a contradiction.
\end{proof}

\section{Harmonic functions}

\begin{definition}
  A function $f \col G \to \R$ is \emph{harmonic}, iff there exists a holomorphic $g \col G \to \C$ such that $\Re g = f$. If $\wt f = \Im g$, $f$ and $\wt f$ are said to be \emph{harmonic conjugates}.
\end{definition}

\begin{lemma}[Laplace's equations]
  If $u+iv \in \Hol G$, then
  $$ u'_{xx} + v'_{yy} = 0. $$
\end{lemma}

\begin{proof}
  From Cauchy-Riemann equations.
\end{proof}

\begin{definition}
  The differential operator
  $$ \Delta = \sum_{j=1}^n \p{\frac{\pd}{\pd x_j}}^2 $$
  is called the \emph{Laplace operator}.
\end{definition}

\begin{definition}
  A function $f \col H \to \R$ is called \emph{harmonic}, iff
  $$ \Delta f = 0. $$
\end{definition}

\begin{theorem}
  If $u \in C^2(G)$ and $\Delta u = 0$, then every $a \in G$ has a neighbourhood $U_a$ such that $u|_{U_a}$ is harmonic.
\end{theorem}

\begin{proof}
  Let $\phi = \frac{\pd u}{\pd x}$ and $\psi = -\frac{\pd u}{\pd y}$. We have
  $$ \frac{\pd \psi}{\pd x} = \frac{\pd \phi}{\pd y}, $$
  so there exists a function $v$ such that $\frac{\pd v}{\pd y} = \phi$ and $\frac{\pd v}{\pd x} = \psi$. This $v$ is harmonically conjugate to $u$, since the Cauchy-Riemann equations are satisfied.
\end{proof}


\section{Integrals of closed forms}

\begin{lemma}
  Suppose $\phi = \d \Phi$ in $G$. Then
  $$ \int_\gg \phi = \Phi(\gg(b)) - \Phi(\gg(a)) $$
  for every path $\gg \col [a, b] \to G$.
\end{lemma}

\begin{proof}
  By the theorem on exact forms.
\end{proof}

\begin{definition}
  A continuous function $F \col [a, b] \to \C$ is called the \emph{antiderivative along a path} $\gg \col [a, b] \to G$ of a 1-form $\phi$, iff for every $t \in [a, b]$ exists an antiderivative $\Phi$ in some neighbourhood $V_t \ni \gg(t)$ such that $F(t) = \Phi \circ \gg(t)$ for all $t \in V_t$.
\end{definition}

\begin{theorem}
  ~\begin{enumerate}
    \item The antiderivative $F$ exists.
    \item If $F_1$ and $F_2$ are two antiderivatives, there exists $c \in \C$ such that $F_1 = F_2 + c$.
  \end{enumerate}  
\end{theorem}

\begin{proof}[Proof of uniqueness]
  It follows from the definition that $F$ is locally constant.
\end{proof}

\begin{proof}[Proof of existence]
  Split $[a, b]$ into small subintervals (small enough for the form $\phi$ to have an antiderivative on the $\gg$-image of each). Choose constants in their intersections in such a way that they make an actual function (antiderivatives differ by a constant).
\end{proof}

\begin{remark}
  This can be used as an alternative definition of the integral along a path:
  $$ \int_\gg \phi := F(b) - F(a). $$
\end{remark}


\section{Homotopies}

\begin{definition}
  A \emph{homotopy} is a continuous map $h \col [\ga, \gb] \times [a, b] \to G$ (usually $\ga = 0$, $\gb = 1$).
\end{definition}

\begin{definition}
  A \emph{loop} is a closed path; i.e. a $\gg \col [a, b] \to \C$ that can be continued to an $(b-a)$-periodic one. A loop is \emph{contractible}, iff it is homotopic to a constant path.
  $G$ is \emph{simply-connected}, iff every loop in $G$ is contractible.
\end{definition}

\begin{example}
  All astroid domains are simply-connected.  
\end{example}

\begin{definition}
  Let $\phi$ be a 1-form in $G$, $S = [0, 1] \times [a, b]$, $h \col S \go G$ a homotopy.
  A continuous $F \col S \to G$ is an \emph{antiderivative of $\phi$ along $h$}, iff for every $(t, s) \in S$ there exists a ball $B \ss G$ with the centre at $h_t(s)$ and an antiderivative $U$ for $\phi$ in $B$.
\end{definition}

\begin{theorem}
  Such $F$ always exists in case of a closed $\phi$.
\end{theorem}

\begin{proof}
  $h(S)$ is compact. By closedness of  $\phi$, take balls such that there exists an antiderivative.
  By continuity of $h$ and Lebesgue's lemma, there exists $\gd > 0$ such that $h(e)$ lies completely in one of these balls for every $e$ of diameter less than $\gd$.
  Extract a finite subcover, and make them agree on intersections.
\end{proof}

\begin{theorem}
  Let $\gg_t$ be a homotopy in $G$, and all paths $\gg_t$ are closed.
  Let $\phi$ be a closed 1-form in $G$, then
  $$ \int_{\gg_0} \phi = \int_{\gg_1} \phi. $$  
\end{theorem}

\begin{proof}
  Define $g(t) = \int_{\gg_t} \phi.$ We assert this function is locally constant.
  Fix $t \in [a, b]$. Then
  $$ \int_{\gg_{t}} \phi = F\p{\gg_{t}(b)}-F\p{\gg_t(a)} \equiv \const $$
  for some antiderivative $F$ along $\gg_t.$ 
\end{proof}

\begin{corollary}
  In a simply-connected set, every closed form is exact.
\end{corollary}

\begin{proof}
  Because the integral over any closed path equals that over a constant one.
\end{proof}


\section{Laurent series}

\begin{definition}
  A \emph{Laurent series} is one of the form
  $$ \sum_{k \in \Z} c_k \p{z-z_0}^k $$
  for some $z, z_0, c_k \in \C$.
  It is said to \emph{converge} at $z$, iff both
  \begin{align*}
    \sum_{k \ge 0} &c_k \p{z-z_0}^k, &
    \sum_{k < 0} &c_k \p{z-z_0}^k
  \end{align*}
  converge at $z$. The first of these is the \emph{regular} part; the other one --- \emph{principal.}
\end{definition}

\begin{theorem}
  Let
  $$ A = \b{ z \in \C \mid r < \a{z-z_0}<R } $$
  (\emph{anneau})
  for some $0< r< R$. 
  If $f \col A \to \C$ is holomorphic, then $f$ decomposes uniquely into a Laurent series at any $z_0 \in A$.
\end{theorem}

\begin{idea}
  Consider integrals over the inner $c$ and outer $C$ components of the boundary of the ring $A$.
  For every $z \in Z$,
  $$ \int_c \frac{f(w)-f(z)}{w-z} \d w = \int_C \frac{f(w)-f(z)}{w-z} \d w. $$
  From this we get an expression for $2\pi i f(z)$ as a sum of integrals of two geometric series.
\end{idea}

\section{Singularities}

\begin{definition}
  Let $f \col G \sm \b{a} \to \C$ be holomorphic, $a \in G$.
  \begin{itemize}
    \item $a$ is \emph{removable}, iff $f$ is bounded in a neighbourhood of $a$.
    \item $a$ is a \emph{pole}, iff $f(z) \to \infty$ when $z \to a$.
    \item $a$ is \emph{essential}, iff it is not removable or a pole; i.e. $f$ has no limit at $a$.
  \end{itemize}
\end{definition}

\begin{lemma}
  Let $a$ be a correctible singularity of $f \col G \sm \b{a} \to \C$.
  Then $f$ can be continued to an analytic function $f \col G \to \C$.
\end{lemma}

\begin{proof}
  We assert every coefficient of the principal part is zero.
  Indeed,
  \begin{align*}
    c_k
    &= \frac{1}{2\pi i} \int_{a+rS^1} f(\gz) \p{\gz-a}^{-j-1} \d \gz, \\
    \\
    \a{c_k}
    &\le \frac{A \a{r}^z{-j-1} 2 \pi r}{2\pi} \\
    &\xrightarrow[r\to 0]{} 0. 
  \end{align*}
\end{proof}

\begin{lemma}
  $a$ is a pole iff
  the number of nonzero coefficients $c_k$ at $a$ with $k < 0$ is nonzero and finite.
  $a$ is essential, iff it is infinite.
\end{lemma}

\begin{idea}
  If $f \to \infty$, then $a$ is c removable for $1/f$.
\end{idea}

\section{Sokhotsky's theorem}

\begin{theorem}[Sokhotsky]
  Let $f \in \Hol G$, and $a$ an essential singularity of $f$.
  Then, for every $\eps > 0$, the set $f\p{B_\eps(a)}$ is dense in $\C$.
\end{theorem}

\begin{proof}
  Suppose otherwise: let $b \in \C$ be such that
  $$ \a{f(z)-b} \ge \gd $$
  for all $z \in B := B_\eps(a)$ for some $\eps > 0$.
  The function
  $$ h(z) := \frac{1}{f(z)-b} $$
  is analytic at $a$ and bounded.
  Then $h$ has a removable singularity at $a$, which allows us to think it is defined in the whole of $B$.
  Hence
  $$ f(z) = \frac{1}{h(z)}+b $$
  has a finite number of negative powers in the Laurent decomposition, which is false.
\end{proof}

\section{Orders of zeroes}

\begin{definition}
  Let $a \in G$.
  Every holomorphic $f \col G \sm \b{a} \to \C$ can be presented as
  $$ f(z) = (z-a)^k g(z), $$
  where $k \in \Z$, $g \in \Hol G$, $g(a) \ne 0$. This $k$ is called the \emph{order} of $a$ in $f$, and denoted
  $$ \ord_a f := k. $$
\end{definition}

\begin{lemma}
  The following are equivalent:
  \begin{enumerate}
    \item $\ord_a f = k$.
    \item $f(a) = f'(a) = \dots = f^{(k-1)}(a) = 0$, $f^{(k)}(a) \ne 0$.
  \end{enumerate}  
\end{lemma}

\begin{proof}
  Since $c_k = \frac{f^{(k)}(z_0)}{k!}.$
\end{proof}

\section{Residues}

\begin{definition}
  Let $a \in G$ be an isolated singularity of $f$,
  $$ f(z) = \sum_{j \in \Z} c_j (z-a)^j $$
  in a ball of radius $r > 0$ around $a$.
  The \emph{residue} of $f$ at $a$ is the number
  $$ \Res_a f := c_{-1} = \frac{1}{2\pi i} \int_{a+rS^1} f(z) \d z. $$
\end{definition}

\begin{lemma}
  If $-m = \ord_a f$ and $m > 0$, then
  $$ \Res_a f = \frac{1}{(m-1)!} \lim_{z \to a} \p{ \p{z-a}^m f(z) }^{(m-1)} $$
\end{lemma}

\begin{proof}
  Exercise.
\end{proof}

\begin{lemma}
  If $f = g/h$ and $\ord_a h = 1$, then
  $$ \Res_a f = \frac{g(a)}{h'(a)}. $$
\end{lemma}

\begin{proof}
  Follows from the previous one.
\end{proof}

\section{Indices}

\newcommand{\Ind}[0]{\on*{Ind}}

\begin{definition}
  Let $\gg \col [0, 1] \to \C$ be a closed path.
  If $a \not\in \im \gg$, then the \emph{index} of $\gg$ relative to $a$ is the number
  $$ \Ind_a \gg := \frac{1}{2\pi i} \int_\gg \frac{\d z}{z - a}. $$
\end{definition}

Full-blown representation theory.

\begin{lemma}
  ~\begin{enumerate}
    \item Index does not change upon homotopies that do not contain $a$ in their image.
    \item Index is an integer.
    \item Index is constant on every connected component of $\C \sm \im \gg$.
  \end{enumerate}
\end{lemma}

\section{The residue theorem}

\begin{definition}
  Let $\Gamma := \b{\gg_1, \dots, \gg_n}$ be closed paths in $G \ss \C$.
  $\gg_\s$ is a \emph{proper path system}, iff for every $f \in \Hol G$ we have
  $$ \int_\Gamma f(z) \d z := \p{\,\int_{\gg_1} + \dots + \int_{\gg_n}\,}\, f(z) \d z = 0. $$
\end{definition}

\begin{theorem}[on residues]
  Let $\Gamma = \b{\gg_1, \dots, \gg_n}$ be a proper path system in $G$,
  $$ f \in \Hol G \sm \b{z_1, \dots, z_k}, $$
  where $z_j \not\in \gg$ for every $j$ and some path $\gg \col [0, 1] \to G$. Then
  $$ \frac{1}{2 \pi i} \int_\Gamma f(z) \d z = \sum_{z \in G} \Res_{z}(f) \Ind_{z}(\Gamma ). $$
\end{theorem}

\begin{proof}
  Let $g_1, \dots, g_k$ be principal parts of Laurent series of $f$ around $\b{z_j}$.
  Then
  $$ g_j(z) = \sum_{s=1}^\infty \frac{c_s}{(z-z_j)^s} $$
   If $s > 1$,
   $$ g_s(z) = \frac{c_{-1}}{z-z_j} + h_s(z), $$
   where $h_s$ has an antiderivative in $G$.
   Integrating this, we get exactly
   $$ \int_{\gg_j} f(z) \d z = \int_{\gg_j} \ub{\p{f(z)-g_j(z)}}_{\text{has no singularity in $z_j$}} \d z + \Res_{z_j}(f) \cdot 2 \pi i \Ind_{z_j}(\gg_j). $$
   Summing this over $j$ and using properness of $\Gamma$, we get the desired.
\end{proof}

\begin{remark}
  This theorem still holds true, if $f$ has an infinite number of singularities $\b{z_j}$, but with discrete induced topology.  
\end{remark}

\section{Change of variables for non-smooth paths}

\begin{lemma}
  Let $F$ be an antiderivative of $f \d z$ along $\gg$.
  Then $F \circ h$ is antiderivative of the same form along $\gg \circ h$.
\end{lemma}

\begin{proof}
  Exercise.
\end{proof}

\begin{lemma}
  Let $G_1, G_2 \ss \C$ be domains, $g \col G_1 \to G_2$ a holomorphic function.
  Let $f \in \Hol G_2$,  and let $\gg$ be a path in $G_1$.
  Then
  $$ \int_{g \circ \gg} f(z) \d z = \int_\gg f \p{g(z)}   \cdot g'(z) \d z. $$
\end{lemma}

\begin{proof}
  If $\gg$ is piecewise smooth, this follows from the change of variables formula. Otherwise, let $F$ be an antiderivative of $f \d z$ along $g \circ \gg$. Differentiating any local antiderivative, we see that it is also an antiderivative of $\p{f \circ g} \cdot g'$ along $\gg$.
\end{proof}

\begin{lemma}
  Index $\Ind_{z_0}(\gg)$ of a continuous $\gg$ is locally constant with respect to $z_0$.
\end{lemma}

\begin{proof}
  From the previous lemma. 
\end{proof}

\begin{lemma}
  If $z_0$ is in an unbounded component of $\C \sm \im \gg$, then $\Ind_{z_0}(\gg) = 0.$
\end{lemma}

\begin{proof}
  $$ \Ind_{z_0} \gg = \frac{1}{2\pi i} \int_{\gg -z} \frac{\d w}{w}. $$
  With $\a{z_0} \to \infty$, $\im \p{\gg-z_0}$ is within a half-plane. 
\end{proof}

\section{Logarithms}

\begin{definition}
  A continuous $\phi \col G \to \C$ is a \emph{branch of a logarithm} in $G$, iff $e^{\phi(z)} = z$ for all $z \in G$.
\end{definition}

\begin{lemma}
  Let $\phi \col G \to \C$ be a logarithm branch.
  \begin{enumerate}
    \item $0 \not\in G$.
    \item $\phi'(z) = 1/z$. In particular, $\phi$ is holomorphic.
  \end{enumerate}
\end{lemma}

\begin{proof}
  ~\begin{enumerate}
    \item Obvious.
    \item From the inverse function theorem.
  \end{enumerate}
\end{proof}

\begin{definition}
  A continuous $\phi \col G \to \C$ is a \emph{branch of a logarithm of $F \col G \to \C$} in $G$, iff $e^{\phi(z)} = F(z)$ for all $z \in G$.
\end{definition}

\begin{theorem}
  If $G$ is simply-connected, and $F \in \Hol G$, $F \ne 0$, then there exists a branch of the logarithm of $F$ in $G$.  
\end{theorem}

\begin{proof}
  There exists an antiderivative $H$ for $F'/F$.
  Differentiating $\p{e^H/F}'$, we get $e^H = c F$ for some $c \in \C$. Then $F = e^{H - \Arg c}$.
\end{proof}

\begin{definition}
  We know that
  $$ F(z) = e^{\Phi(z)}. $$
  There is $\phi$ such that
  $$ \Phi(z) = \log \a{F(z)} + i \phi(z), $$
  where $\phi$ is some continuous $G \to \C$. 
  This $\phi$ is called a \emph{branch of the argument of $F$}.
\end{definition}

\begin{definition}
  A continuous $u \col [0, 1] \to \C$ is a \emph{branch of a logarithm} along $\gg [0, 1] \to \C$, iff $u \circ \gg (t)$ is a logarithm of $F\circ \gg (t).$ Likewise for \emph{argument}. 
\end{definition}

\begin{theorem}
  In the conditions of the definition, there exists a logarithm branch of $F$, and any two such differ by $2 \pi i k$ for some $k \in \Z$. 
\end{theorem}

\begin{proof}
  Uniqueness: $u_1 - u_2$ is a continuous function $[0, 1] \to 2 \pi i \Z$.
  Existence follows from local existence.
\end{proof}

\begin{lemma}
  There exists a continuous argument branch.
\end{lemma}

\begin{proof}
  We can find one knowing a continuous logarithm branch.
\end{proof}

\begin{lemma}
  Index is an integer.
\end{lemma}

\begin{proof}
  Choose a continuous logarithm branch and use uniqueness locally.
\end{proof}

\section{Jordan's curve theorem}

\begin{theorem}
  Let $\gg \col [0, 1] \to \C$ be a simple closed path. Then $\C \sm \im \gg$ consists of two connected components.
\end{theorem}

\begin{proof}
  
\end{proof}

\section{The argument principle}

\begin{definition}
  Let $\gg$ be a simple closed path in $G$ such that $\C \sm \im \gg$ splits into two connected components. The bounded of these two is called \emph{Jordan}.
\end{definition}

\begin{theorem}
  Let $f$ be holomorphic in a neighbourhood of a $\gg$-Jordan $\Cl G$, except a finite number of poles which are not in $\im \gg$. Then
  $$  \diff{\frac{1}{2 \pi} \Arg \circ f \circ \gg}_0^1 = \sum_{z \in G} \ord_{z}(f). $$
\end{theorem}

\begin{proof}
  On the left we have
  \begin{align*}
    \Delta
    &= \frac{1}{2 \pi i} \int_\gg \frac{f'(z)}{f(z)} \d z \\
    &= \sum_{z \in G} \Res_z\p{\frac{f'}{f}} \Ind_z(\gg) \\
    &= \sum_{z \in G} \Res_z\p{\frac{f'}{f}} \\
    &= \sum_{z \in G} \ord_z\p{\frac{f'}{f}}.
  \end{align*}
  The last equality is easy to check directly.
\end{proof}

\section{The theorem of Rouché}

\begin{theorem}[Rouché]
  Let $G$ be a $\gg$-Jordan domain. 
  Let $f, g$ be holomorphic in a neighbourhood of $\Cl G$.
  Suppose that
  $$ \fa z \in \im \gg \col \a{f(z)} > \a{g(z)}. $$
  Then $f$ and $f+g$ have the same number of zeroes in $G$.
\end{theorem}

\begin{idea}
  Use the previous theorem to compute the difference  in sums of multiplicities as an integral of some $f'/f$. The condition on modules is needed to divide through $f$, and compute $\Ind_0 \phi \circ \gg$, where $\phi(z) = 1+g(z)/f(z)$.
\end{idea}

\section{The Riemann sphere}

\begin{definition}
  $\wh \C := \C \sqcup \b{\infty}$.
  A basis of nbhds of $\infty$ is formed by
  $$ \b{ \b{z \mid \a{z} > R} \mid R \in \R}. $$
\end{definition}

\begin{definition}
  Let $f$ be defined in a neighbourhood of $\infty$.
  $f$ is \emph{holomorphic at $\infty$}, iff $f(1/z)$ is holomorphic in a neighbourhood of 0.
\end{definition}

\begin{definition}
  Let $f$ be holomorphic at $\infty$.
  Then
  \begin{align*}
    \Ind_\infty(\gg) &:= \Ind_0(1/\gg), \\
    \Res_{\infty}(f) &:= -\Res_{z \to 0}\frac{f(1/z)}{z^2}.
  \end{align*}
\end{definition}

The basis for this definition is the fact that
$$ \Res_\infty(f) \Ind_\infty(\gg) = \int_{1/\gg} -\frac{f(1/z)}{z^2} \d z = \int_\gg f(z) \d z $$
for any $\gg$ not through zero.

\section{Another theorem on residues}

\begin{theorem}
  If $f \in \Hol \C \sm \b{z_1, \dots, z_k}$, then
  $$ \sum_{z \in \C} \Res_z(f) = 0. $$  
\end{theorem}

\begin{proof}
  Observe that, if $\gg$ is the circle around 0 of sufficiently large radius, $1/\gg$ is passed in the opposite direction. Then
  \begin{align*}
    \frac{1}{2 \pi i} \int_\gg f(z) \d z
    &= \Res_\infty(f) \Ind_0 \frac{1}{\gg} \\
    &= -\Res_\infty(f). 
  \end{align*}
\end{proof}

\section{Univalent functions}

\begin{definition}
  A function is \emph{univalent}, iff it is holomorphic and injective.
\end{definition}

\begin{theorem}
  Let $f \col G \to \C$ be univalent.
  Then $f'$ is nowhere zero.  
\end{theorem}

\begin{remark}
  The converse is not true even for holomorphic functions.  
\end{remark}

\begin{proof}
  Suppose $f'(z_0) = 0$.
  $$ f(z) = f(z_0) + (z-z_0)^k g(z), $$
  where $k > 1$, $g(z_0) \ne 0$.
  In a sufficiently small ball $B \ni z_0$, $g$ is nonzero and there is a logarithm $h \col B \to \C$ of $g$:
  $$ g(z) = e^{h(z)}. $$
  Then
  $$ f(z) = f(z_0) + \p{(z-z_0) \wt g(z)}^k, $$
  where
  $$ \wt g(z) = e^{\frac{h(z)}{k}}. $$
  The function $\phi(z) = (z-z_0) g(z)$ is univalent in a a neighbourhood of $z_0$ by a theorem from real analysis:
  $$ \phi'(z) = g(z) + (z-z_0) g'(z_0) \ne 0 \text{ when $z = z_0$}. $$
  This means that, if $z_1$ is sufficiently close to $f(z_0)$, $\phi$ is injective, and the equation
  $$ \p{\phi(z)}^k = z_1-f(z_0) $$
  has $k$ solutions in $z$.
  This contradicts univalence of $f$:
  $$ f(z) = \p{\phi(z)}^k. $$
\end{proof}

\begin{lemma}
  If $f \col G \to \C$ is univalent, then $f$ is open.
\end{lemma}

\begin{proof}
  Maps with non-degenerate differentials are open.
\end{proof}

\section{Conformal maps}

\begin{definition}
  We say a map $f \col G \to \C$ is \emph{conformal}, iff
  $$ \Arg(\ol{z_1} z_2) = \Arg\p{\ol{f'(z_0)z_1} \cdot f'(z_0)z_2} $$
  for all $z_0, z_1, z_2 \in G$.
  That is, conformal maps preserve angles between tangent vectors.
  In fact, this is (easy to see) equivalent to univalence.
\end{definition}

\begin{theorem}[Riemann]
  The following conditions are equivalent:
  ~\begin{enumerate}
    \item $G$ is simply-connected and $\C \ne G$.
    \item Exists an univalent map $G \to \Int \mathbb{D}$.
  \end{enumerate} 
\end{theorem}

\begin{proof}[$\Leftarrow$]
  From Liouville's theorem.
\end{proof}

\begin{proof}[$\Rightarrow$]
  In April.
\end{proof}

\section{Automorphisms}

\subsection{Automorphisms}

\begin{definition}
  Any univalent $f \col G \to G$ we'll call an \emph{automorphism} of $G$. 
\end{definition}

\begin{theorem}
  \label{automorphisms of C}
  Any automorphism of $\C$ is an affine map
  $$ z \mapsto az + b. $$
\end{theorem}

The converse is trivially true.

\begin{proof}
  Let $f \in \Aut \C$.
  If infinitely many coefficients in the Taylor expansion are nonzero, $\infty$ is an essential singularity for $f$. By Sokhotsky's theorem, for any ball $B \ni 0$ we have
  $$ f(B) \cap f(\C \sm B) \ne \naught. $$
  Hence $f$ is a polynomial. But $f'$ is nowhere zero by one of the previous theorems, which means $f$ is affine.
\end{proof}

\subsection{Automorphisms of $\wh \C$}

\begin{definition}
  A \emph{Möbius transform} is a function of form
  $$ f\col z \mapsto \frac{az+b}{cz+d}, $$
  where $ad \ne bc$.
\end{definition}

As we can see, $f(-d/c) = \infty$ and $f(\infty) = a/c$.

\begin{lemma}
  Möbius transforms form a group with respect to composition.
\end{lemma}

\begin{proof}
  Routine check.
\end{proof}

\begin{lemma}
  \label{transitive subgroup that contains a stabiliser is the whole G}
  Let $G$ be acting on a set $X$.
  Let $H \le G$ be acting transitively.
  Suppose $H \sps \Stab_G(x)$ for some $x \in X$.
  Then $H = G$.
\end{lemma}

\begin{proof}
  Let $g \in G$. Since the action of $H$ is transitive, there exists $h \in H$ such that
  $ hgx = x. $
  Then $hg \in \Stab_G(x) \ss H$, and so $h^{-1} \cdot hg = g \in H$.
\end{proof}

\begin{theorem}
  The group of Möbius transforms is not smaller than $\Aut \wh \C$.
\end{theorem}

\begin{proof}
  Let $M$ be the group of Möbius transforms, and let $S \le \Aut \wh \C$ be the stabiliser of $\infty$.
  It is easy to see that $M$ acts transitively.
  $S \le M$, since every $s \in S$ also leaves in place the $\C$, and so must be an affine function (page \pageref{automorphisms of C}).
\end{proof}

\subsection{Disk automorphisms}

Let $D := \Int \D^2$.

\begin{definition}
  Let $N$ be the set of maps of form
  $$ f_{a,c} \col z \mapsto c \cdot \frac{z+a}{\ol a z+1}, $$
  where $\a{a} < 1$ and $\a{c} = 1$.
\end{definition}

\begin{lemma}
  $f_{a,c}(D) \ss D$.
\end{lemma}

\begin{proof}
  Ultimately, it follows from the maximum modulus principle.
\end{proof}

\begin{lemma}
  $N$ is a group.
\end{lemma}

\begin{proof}
  ~\begin{enumerate}
    \item For the identity map, put $a = 0$ and $c = 1$. 
    \item The inverse is of the same form (routine algebra).
    \item The composition too (same).
  \end{enumerate}
\end{proof}

\begin{lemma}[Schwartz]
  Let $f \col D \to D$ be an analytic function, $f(0) = 0$.
  Then $\a{f(z)} \le \a{z}$ for all $z \in D$.
  If the equality is reached for some $z \ne 0$, then exists $\ga \in D$ such that $f(z) = \ga z$ for all $z$.
\end{lemma}

In particular, $N \ge \Stab_{\Aut D}(0)$.

\begin{proof}
  Suppose $f$ is analytic in some ball of radius $R > 1$ with centre at 0.
  Let $g(z) := f(z)/z$.
  $g$ is holomorphic with $\a{z} < R$ and $z \ne 0$.
  $g$ can be continued to an analytic function in the ball of radius $R$ around 0 (including 0).
  If $\a{z} = 1$, then, by passage to the limit,
  $$ \a{g(z)} = \a{f(z)}/\a{z} = \a{f(z)} \le 1. $$
  By the maximum modulus principle, the conclusion holds.
  
  In the general case, consider $f_r(z) := f(rz)$.
  $f_r$ is defined and holomorphic with $\a{rz} < 1$; that is, when $\a{z} < 1/r =: R$.
  For sure, $R > 1$.
  By the case already considered, $\a{f_r(z)} \le \a{z}$ for all $z \in D$, and so $\a{f(rz)} \le \a{z}$ for all $z$ with $\a{z} < 1$.
  
  Suppose now, the equality is reached for some $z \in D \sm \b{0}$.
  Since $z$ is internal for $D$, $g$ must be constant by the maximum modulus principle.
\end{proof}

\begin{theorem}
  $N = \Aut D$.
\end{theorem}

\begin{proof}
  We show that $N$ contains the stabiliser of zero.
  Let $\phi \in \Aut D$, $\phi(0) = 0$.
  By the Schwartz's lemma, $\a{\phi(z)} \le \a{z}$ for all $z \in D$.
  By symmetry,
  $ \a{\phi^{-1}(z)} \le \a{z} $
  for all $z \in D$.
  Then $\a{z} = \a{\phi^{-1} \circ \phi(z)} \le \a{\phi(z)}$, so $\phi(z) = \a{z}$ everywhere in $D$.
  
  To see that $N$ acts transitively, observe that $f(a) = 0$ and $f(0) = -ca$ for every $f\in N$.
  Now we can apply the lemma from page \pageref{transitive subgroup that contains a stabiliser is the whole G}.
\end{proof}

\section{Examples of conformal maps}

\begin{lemma}
  Let $\Pi_- = \b{z \in \C \mid \Re(z) < 0}$, $\psi \col z \mapsto \frac{z-a}{z+\ol a}$, $\Re a < 0$.
  Then
  $$ \psi(\Pi_-) = D. $$
\end{lemma}

\begin{proof}
  It is straightforward to show that $\psi(\Pi_-) \ss \D$.
  Likewise, $1/\psi(\Pi_+) \ss D$.
  Hence $\phi(\Pi_-) \ss D$, $\phi(\Pi_+) \ss \wh \C \sm \D$, $\phi(i \R) \ss \S^1$.
  Since $\phi$ is an automorphism, this implies the desired.
\end{proof}

\begin{lemma}
  All Möbius transforms map circles on the Riemann sphere into circles.
\end{lemma}

\begin{proof}
  The maps $z+a, az, 1/z$ generate $\Aut \wh \C$ --- for them it is obvious.
\end{proof}

\begin{lemma}
  A Möbius transform is uniquely determined by images of three points.
\end{lemma}

\begin{proof}
  $$
  \frac{\frac{z-z_1}{z-z_2}}{\frac{z_3-z_1}{z_3-z_2}}
  =
  \frac{\frac{w-w_1}{w-w_2}}{\frac{w_3-w_1}{w_3-w_2}}.
  $$
\end{proof}

\section{Convergence of analytic functions}

\begin{definition}
  We say that a sequence $\b{f_n} \ss \Hol G$ \emph{converges compactly} to $f \col G \to \C$, iff, for every compact $K \ss G$,
  $$ f_n|_K \rightrightarrows f|_K. $$
\end{definition}

\begin{example}
  Let $G = \b{z \mid \a{z} < 1}$.
  The sequence $f_n = \frac{1}{n} \cdot \frac{1}{1-z^2}$ converges pointwise, but not uniformly; hence does not converge in the above sense.   
\end{example}

\begin{theorem}[1st of Weierstrass]
  If $f_n \to f$ compactly, then $f$ is holomorphic in $G$.
\end{theorem}

\begin{proof}
  By Stokes-Seidel theorem, $f$ is continuous.
  We show that the integral over the boundary $B$ of any rectangle in $G$ is zero; then the theorem follows from the Cauchy's theorem on closedness, page \pageref{Cauchy, on closedness}.
  Observe that
  \begin{align*}
    \a{\ \int_{B} f(z) \d z - \int_B f_n(z) \d z\ }
    &\le \max_{z \in B} \a{f(z)-f_n(z)} \cdot \const \\
    &\xrightarrow[n \to \infty]{} 0.
  \end{align*} 
  But the integral over any $f_n$ is zero (they are analytic in $G$).
\end{proof}

\begin{theorem}[2nd of Weierstrass]
  If $f_n \to f$ compactly, then $f_n' \to f'$ compactly.
\end{theorem}

\begin{proof}
  Let $K$ be a closed ball of radius $r$ with centre at some $z_0$, $\ol K \ss G$, $\gg := \pd K$.
  $$ f'_n(z) = \frac{1}{2 \pi i} \int_{\gg} \frac{f(\gz) \d \gz}{(\gz-z)^2}. $$
  When $z \in \ol K$, the denominator is nonzero, so $f_n' \rightrightarrows f'$ on $K$.
  
  If $K$ is a general compact set, we can cover it with a finite number of balls and do the same.
\end{proof}

\section{Normal families}

\begin{definition}
  Let $G$ be a domain, $F$ a set of functions on $G$.
  $F$ is \emph{normal}, iff
  \begin{align*}
    \fa \text{compact } K \ss G\ 
    \ex c > 0\ 
    \fa f \in F\ 
    \col \a{f|_K} < c.
  \end{align*}
\end{definition}

\begin{lemma}
  If $F$ is normal, then $F' := \b{f' \mid f \in F}$ is normal.
\end{lemma}

\begin{proof}
  Repeats the proof of the second theorem of Weierstrass.
\end{proof}

\begin{theorem}[Montel]
  Equivalent are:
  \begin{enumerate}
    \item $F$ is normal.
    \item Any sequence $\b{f_n}$ with $f_n \in F$ has a compactly convergent subsequence.
  \end{enumerate}  
\end{theorem}

\begin{proof}[$2 \Rightarrow 1$]
  Suppose otherwise: on some compact the functions $f_n$ are not uniformly bounded; i.e., there is a diverging (in this sense) sequence of functions. But they have 
\end{proof}

\begin{proof}[$1 \Rightarrow 2$]
  For every $f \in F$, $z_1, z_2 \in G$,
  $$ \a{f(z_2)-f(z_1)} \le \sup_{\xi \in [z_1, z_2]} \a{f'(\xi)} \cdot \a{z_2-z_1} \le c \a{z_2-z_1} $$
  for some $c > 0$, since the set $T_\gd := \b{z\in G \mid \dist(z, E) \le \gd}$ is compact, and we can bound $F'$ on $T_\gd$ by its normality and the previous lemma.
  Therefore, $F$ is uniformly equicontinuous.
  The Arcela--Askoli theorem states it must be uniformly bounded.
  
  Now we apply the diagonal process.
  Let $E_1 \ss E_2 \ss \dots$ be an exhausting sequence of compacts for $G$ (that is, $E_j \ss \Int E_{j+1}$ and $\bigcup E_j = G$).
  Let $\b{f^m_n}$ be a family of sequences such that $\b{f^{m+1}_n}$ is a subsequence of $\b{f^m_n}$ that converges on $E_m$.
  Then the diagonal sequence $\b{f^n_n}_n$ converges on every of $E_\s$.  
\end{proof}

\section{Analytic continuation}

Let $f \col G \to \C$ be analytic.
How easy is it continue outwards of $G$?

\begin{definition}
  Let $G_1, G_2 \ss \C$ be domains such that $G_1 \cap G_2$ is also connected.
  Let $f_i \in \Hol G_i$ for $i \in \b{1, 2}$.
  $f_2$ is said to be a \emph{direct continuation} of $f_1$ onto $G_2$, iff $f_1 = f_2$ on $G_1 \cap G_2$.
\end{definition}

\begin{definition}
  $G$ is said to be a \emph{natural domain} for $f \in \Hol G$, iff $f$ does not admit a direct continuation onto a larger domain $G' \supset G$.
\end{definition}

\begin{theorem}[Hadamard]
  The unit disk $D := \Int \D^2$ is the natural domain of
  $$ f \col z \mapsto \sum_{n=1}^\infty z^{n!}. $$
\end{theorem}

\begin{proof}
  This series indeed converges in $D$.
  If $f$ can be continued to something larger, let $G$, this $G$ contains $z_0 \in \S^1$.
  Let $\gz := e^{2 \pi i \ga}$ be lying on $\S^1 \cap G \ni$, with $\ga =: p/q \in \Q$.
  Exists $\lim_{r \to 1-} f(r \gz)$.
  But then $f(r\gz) \xrightarrow[r \to 1-]{} \infty$ (the addends become large from the $q$th one).
\end{proof}

\begin{definition}
  A pair $(G, f)$, where $f \in \Hol G$ and $G$ is a ball with centre at some $z_0$, is called an \emph{element} of an analytic function. If the radius of $r$ is maximal, the element is called \emph{natural}. 
\end{definition}

Of course, $G$ may not be the natural domain for $f$.

\begin{definition}
  Let $(D_1, f_1), (D_2, f_2)$ be elements.
  The second of the them is the \emph{continuation} of the first one along some path $\gg$, iff exists $\phi \col [0,1] \to \C$ such that for every $t \in [a,b]$ there exists an element $(D_t, f_t)$ of an analytic function, with $D_t$ having the centre at $\gg(t)$, such that $\phi(s) = f_t\p{\gg(s)}$ for all $s \in \gg^{-1}(D_t)$.
\end{definition}

The function $\phi$ is as smooth as the path $\gg$. 